\href{http://www.sigcomm.org/content/ebook}{Recent Advances in Networking}

### 2013-07-28 Compiled/chapter1/ebook.tex
Full compiled
common latex and bibtex styles for all chapters
added page numbers and initial support for copyright, urls are now clickable
fixes

% This work is licensed under
% http://creativecommon.org/licenses/by/3.0/
\documentclass{article}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{color}
\usepackage{url}
\hyphenation{wrap-around}

@@

\author{
Pamela Zave \\
AT\&T Laboratories---Research \\
Florham Park, New Jersey, USA \\
{\tt pamela@research.att.com}
\and
Jennifer Rexford \\
Princeton University \\
Princeton, New Jersey, USA \\
{\tt jrex@cs.princeton.edu}
}

\begin{document}
\thispagestyle{empty}
\maketitle

@@

\bibliographystyle{IEEEtran}
\bibliography{ebook}

>>>>

% This work is licensed under
% http://creativecommon.org/licenses/by/3.0/
\documentclass{article}

\input{../commonstyle}

\input{copyright}

\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{color}
\usepackage{url}
\usepackage{hyperref}
\usepackage{fullpage}
\hyphenation{wrap-around}

@@

\author{
\href{http://www2.research.att.com/~pamela/}{Pamela Zave} \\
%AT\&T Laboratories---Research \\
%Florham Park, New Jersey, USA \\
%{\tt pamela@research.att.com}
\and
\href{http://www.cs.princeton.edu/~jrex/}{Jennifer Rexford} \\
%Princeton University \\
%Princeton, New Jersey, USA \\
%{\tt jrex@cs.princeton.edu}
}

\date{}
\begin{document}

\copyrightstatement

\pagestyle{empty}

\maketitle

\thispagestyle{empty}

@@

%\bibliographystyle{IEEEtran}
\input{../commonbibstyle}
\bibliography{ebook}

### 2013-07-28 Compiled/chapter6/main.tex
Full compiled
common latex and bibtex styles for all chapters
added page numbers and initial support for copyright, urls are now clickable
copyright boxes in all chapters
fixes

\documentclass{article}
\usepackage{amsfonts,amsmath,amssymb}
\interdisplaylinepenalty=2500

\usepackage{graphicx}
\usepackage{multirow}
\usepackage{array}
\usepackage{fancyvrb}
\usepackage{boxedminipage}
\usepackage{color}
\usepackage{paralist}
\usepackage{algorithmic}
\usepackage{slashbox}
\usepackage{xspace}
\usepackage{url}
\usepackage{subfigure}
\usepackage{marginnote}

@@

\author{Luca Cittadini \and Giuseppe Di Battista \and Maurizio Patrignani}

\date{~}

@@

\newpage

\tableofcontents

\newpage

@@

\bibliographystyle{plain}
\bibliography{bibliography}

>>>>

\documentclass{article}
\input{../commonstyle}

\input{copyright}

\usepackage{amsmath,amssymb}
\interdisplaylinepenalty=2500

\usepackage{graphicx}
\usepackage{multirow}
\usepackage{array}
\usepackage{fancyvrb}
\usepackage{boxedminipage}
\usepackage{color}
\usepackage{paralist}
\usepackage{algorithmic}
\usepackage{slashbox}
\usepackage{xspace}
\usepackage{hyperref}
\usepackage{url}
\usepackage{subfigure}
\usepackage{marginnote}

@@

\author{\href{http://www.dia.uniroma3.it/~compunet/www/view/person.php?id=cittadini}{Luca Cittadini} \and \href{http://www.dia.uniroma3.it/people/gdb/}{Giuseppe Di Battista} \and \href{http://www.dia.uniroma3.it/~patrigna/}{Maurizio Patrignani}}

\date{}

\copyrightstatement

\pagestyle{empty}

@@

@@

%\bibliographystyle{plain}

\input{../commonbibstyle}
\bibliography{bibliography}

### 2013-07-28 Compiled/ebook.tex
fixes
fix
added c4 figs

\usepackage[final]{pdfpages}

@@

\title{Recent Advances in Networking}

\author{
Hamed Haddadi,  Olivier Bonaventure (Editors)\\
}

@@

\includepdf[pages=-,pagecommand=\thispagestyle{plain}]{chapter1/chapter1.pdf}
\includepdf[pages=-,pagecommand=\thispagestyle{plain}]{chapter2/chapter2.pdf}
\includepdf[pages=-,pagecommand=\thispagestyle{plain}]{chapter3/chapter3.pdf}
\includepdf[pages=-,pagecommand=\thispagestyle{plain}]{chapter4/chapter4.pdf}
\includepdf[pages=-,pagecommand=\thispagestyle{plain}]{chapter5/chapter5.pdf}
\includepdf[pages=-,pagecommand=\thispagestyle{plain}]{chapter6/chapter6.pdf}
\includepdf[pages=-,pagecommand=\thispagestyle{plain}]{chapter7/chapter7.pdf}
\includepdf[pages=-,pagecommand=\thispagestyle{plain}]{chapter8/chapter8.pdf}
\includepdf[pages=-,pagecommand=\thispagestyle{plain}]{chapter9/chapter9.pdf}

>>>>

\usepackage[final]{pdfpages}
\usepackage{url}
\usepackage{hyperref}
\usepackage{titlepic}

@@

\title{\href{http://www.sigcomm.org/content/ebook}{Recent Advances in Networking}}

\author{
\href{http://www.eecs.qmul.ac.uk/~hamed/}{Hamed Haddadi},  \href{http://www.uclouvain.be/olivier.bonaventure}{Olivier Bonaventure} (Editors)\\
\\
\\
\href{http://www.sigcomm.org/}{ACM SIGCOMM}
}

\titlepic{\includegraphics[width=3cm]{intro/sigcomm-logo-new}}

@@

\includepdf[pages=-,pagecommand=\thispagestyle{plain}]{chapter7/chapter7.pdf}
\includepdf[pages=-,pagecommand=\thispagestyle{plain}]{chapter5/chapter5.pdf}
\includepdf[pages=-,pagecommand=\thispagestyle{plain}]{chapter8/chapter8.pdf}
\includepdf[pages=-,pagecommand=\thispagestyle{plain}]{chapter2/chapter2.pdf}
\includepdf[pages=-,pagecommand=\thispagestyle{plain}]{chapter3/chapter3.pdf}
\includepdf[pages=-,pagecommand=\thispagestyle{plain}]{chapter6/chapter6.pdf}
\includepdf[pages=-,pagecommand=\thispagestyle{plain}]{chapter4/paper.pdf}
\includepdf[pages=-,pagecommand=\thispagestyle{plain}]{chapter1/chapter1.pdf}
\includepdf[pages=-,pagecommand=\thispagestyle{plain}]{chapter9/chapter9.pdf}
